\section{Installation in Visual Studio}
\subsection{Prerequisites}
This installation tutorial is tested on
\begin{enumerate}
\item Visual Studio 2005 on Windows XP
\item Visual Studio 2008 on Windows 7
\end{enumerate}

\subsection{Dependencies}
\subsubsection{Boost}
To compile RobWork you need to have Boost installed. If not already installed or in doubt please visit the \emph{Boost Installation} page.


\subsubsection{Xerces}
You can download Xerces from \lstinline{http://xerces.apache.org/xerces-c/}. If in doubt visit the \emph{Xerces Installation} page.

\subsubsection{Qt}
If you do not already have QT and the QT Visual Studio Add-on installed visit the \emph{QT Installation} section.


\subsection{Setting up Environment Variable}
The Visual Studio projects needs to following Windows Environment Variables:

\begin{description}
\item[ROBWORK\_DIR] Points to the common directory containing RobWork RobWorkStudio etc.. (E.g. \lstinline{c:\rw\})
\item[RW\_BOOST\_ROOT] Points to the Boost folder (e.g. \lstinline{c:\local\boost_1_42}).
\item[RW\_XERCES\_VS\_ROOT] Points to the Xerces folder \\
(e.g. \lstinline{c:\local\xerces-c-3.1.1-x86_64-windows-vc-9.0}).
\item[QTDIR] Points to the QT directory containing the src folder. This variable may already be setted depending on how you have installed QT.
\end{description}


\subsection{Compiling RobWork}
Open the \lstinline{RobWork.sln} file which can be found in
\begin{lstlisting}
c:\RobWork\projects\VisualStudio200X\RobWork
\end{listlisting}
and compile by selecting \lstinline{Build > Build Solution} in the menu.

\subsection{Compiling RobWorkStudio}
The RobWorkStudio solution includes all necessary RobWork packages. It is therefore not necessary to compile the RobWork solution before compiling the RobWorkStudio Solution.

To compile RobWorkStudio, open the RobWorkStudio.sln file which can be found in
\begin{lstlisting}
c:\RobWorkStudio\projects\VisualStudio200X\RobWorkStudio
\end{lstlisting}
and compile by selecting \lstinline{Build > Build Solution}.


\subsection{Using CMake}

Precompiled Lapack and Blas libraries are included in the RobWork
package in the directory \lstinline{RobWork/ext/libs_vs}. You must either add
this directory to the Windows PATH environment variable or copy the
DLL files of this directory to a directory already in the system path.

To see a list of all compilers supported by CMake, type \lstinline{cmake} in a
command window. For this example, we assume the compiler used is Visual
Studio 8 2005.

In the RobWork directory, run the command:
\begin{lstlisting}
cmake -G "Visual Studio 8 2005"
\end{lstlisting}

This CMake command generates a Visual Studio solution file named \lstinline{RobWork.sln}. Open the solution file with Visual Studio and build the
solution. Repeat the procedure for the \lstinline{RobWorkStudio}.
