\section{QT Installation}

\subsection{Linux}
Run your favorite package manager application and install the following packages.

On Ubuntu 10.04
\begin{itemize}
\item
\item 
\item
\end{itemize}
The names of packages and the version may vary depending on the Linux distribution.


\subsection{Windows MinGW}

\subsection{Windows Visual Studio 2008}
Download Qt libraries for Windows (VS 2008) from http://qt.nokia.com/downloads and the Visual Studio Add-in (to be found at the same page under Other Downloads).

First install the QT libraries and secondly the Visual Studio Add-on.

\subsection{Windows Visual Studio 2005}
Unfortunately QT does not have a binary distribution for Visual Studio 2005. You therefore need to download the Qt SDK for Windows and compile QT yourself. 

Testet with:  Visual Studio 2005, QT 2009.04 and QT Visual Studio Addin 1.1.0

Building QT for Visual Studio

\begin{enumerate}
\item Download and install QT Open Source for Windows. You do not have to install the MinGW toolset.
\item Open a command promt and goto the \lstinline{c:\qt\2009.04\qt} folder
\item Run the \lstinline{VCVARS32.BAT} (found in e.g. \lstinline{C:\Program Files\Microsoft Visual Studio 8\VC\bin}) to setup the Visul Studio ToolSet.
\item Run 
\begin{lstlisting}
   configure -no-sql-sqlite -no-qt3support -no-webkit -platform win32-msvc2005. 
\end{lstlisting}   

It is important to specify \lstinline{-platform win32-msvc2005} to tell which toolset to use. The remaining options might be choosen differently.
\item Call \lstinline{nmake} to build QT for visual studio
\item Add \lstinline{c:\qt\2009.04\qt} to your \lstinline{PATH} environment variable
\end{enumerate}
 
Installing QT Visual Studio Addin

\begin{enumerate}
\item Download and install the QT Visual Studio Addin
\item Add the environment variable \lstinline{QTDIR=c:\qt\2009.04\qt}
\item Start Visual Studio
\item Select the menu \lstinline{QT -> QT} Options and make sure the QT Version points to the right directory
\end{enumerate}

You are now ready to build QT applications with Visual Studio

If you have problems compiling please visit: \lstinline{http://dcsoft.com/community\_server/blogs/dcsoft/archive/2009/03/06/how-to-setup-qt-4-5-visual-studio-integration.aspx}
for further information.